
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 2.  Operations on Numeric Vectors"
---

***Note*:** *This problems make uses of the element-to-element property of operations on numeric vectors to calculate pattern summation.* 

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2020_assignment2.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Sample Codes***: You can find similar codes for this assignment here [link](fa2020_assignment2_sample_code.html)


***Submissions***: Submit the link on Github of the assignment to Canvas under Assignment 2. 


Problems
-------
-------


1. Calculate: 


$$
S = 1 + 4 + 7 + 11 +... + 100
$$
```{r, include=FALSE, echo=FALSE, results=FALSE}
x <- seq(1, 100, 3)
sum(x)


```


2. Calculate: 


$$
S = 1^{2020} + 2^{2020} + 3^{2020} +...+2020^{2020}
$$
```{r, include=FALSE, echo=FALSE, results=FALSE}
x <- c(1:2020)
sum(x^2020)
```

3. Calculate: 

$$
S = \frac{1}{1\cdot 2}+\frac{1}{2 \cdot 3}+...+\frac{1}{2020\cdot 2021}
$$
```{r}

z <- sum(1/c(1*2:2021)) # First way I tried solving the problem

x <- sum(1/seq(1*2,2021)) # Written a different way using the sequence function
print(x)
print(z)
```


4. Calculate: 

$$
S = \frac{1}{1\cdot 2 \cdot 3}+\frac{1}{2 \cdot 3 \cdot 4}+...+\frac{1}{2020\cdot 2021 \cdot 2022}
$$
```{r}
x <- 0+1
y <- x+1
z <- y+1

a <- sum(1/seq(x*y*z,2022))
print(a)

```

5. Calculate: 

$$
S = 1^1 + 3^3 + 5^5 + 7^7 +....+2021^{2021}
$$
```{r}


a <- seq(1,2021,2)

b <- a^a

z <- sum(b)
print(z)

```
