
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 3.  Working with Data Frame. Base R Style"
---

***Note*:** *This assignment practices working with Data Frame using Base R.*

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment3.Rmd)) in Rstudio. 

- Right under each question, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas under Assignment 3. 

-------

Problems
-------
 \

1. Create the following data frame

| Rank 	| Age 	| Name  	|
|------	|-----	|-------	|
| 0    	| 28  	| Tom   	|
| 1    	| 34  	| Jack  	|
| 2    	| 29  	| Steve 	|
| 3    	| 42  	| Ricky 	|

```{r}

df = data.frame(Rank = c('0','1','2','3'),
                Age = c(28,34,29,42),
                Name = c('Tom','Jack','Steve','Ricky'))
```


2. Use `read.csv` to import the Covid19 Vaccination data from WHO: [link](https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv)

```{r}
df1 <- read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-states.csv')
```


Show the names of the variables in the data
```{r}
names(df1)



```


3. How many columns and rows the data have? 
```{r}
ncol(df1)
nrow(df1)

str(df1)


```



4. How many missing values are there?   
```{r}
sum(is.na(df1))

```
Show the missing values by columns.
```{r}
colSums(is.na(df1))
```

What variable has the most number of missing values?
```{r}
colMeans(is.na(df1))
```


5. What is the class of the `date` column.  

```{r}
class(df1$date)

```

Change the `date` columns to `date` type using the `as.Date` function.

```{r}
df1$date = as.Date(df1$date)

```

Show the new class of the `date` column.

```{r}
class(df1$date)
```


6. Capitalize the names of all the variables
```{r}
names(df)[1] <- 'Date_report'

```


7. Find the average number of cases per day. 
```{r}

mean(df1$cases, na.rm=TRUE)


```

Find the maximum cases a day.  
```{r}

max(df1$cases, na.rm=TRUE)

```


8. How many states are there in the data?
```{r}
table(df1$state)
```


9. Create a new variable `weekdays` to store the weekday for each rows.
```{r}


```


10. Create the categorical variable `death2` variable taking the values as follows

- `has_death` if there is a death that day
-  `no_death` if there is no death that day

Find the frequency and relative frequency of `no_death` and `has_death`. 

11. Find the first quartile (Q1), second quartile (Q2) and and third quartile (Q3) of the variable `death`. (Hint:  Use the `summary` function)

12. Create the categorical variable `death3` variable taking the values as follows

- `low_death` if the number of deaths smaller than the 25 percentile (Q1)

- `mid_death` if the number of deaths from Q1 to Q3

- `high_death` if the number of deaths greater than Q3

13. Find the average cases in Rhode Island in 2021

14. Find the median cases by weekdays in Rhode Island in 2021 

15. Compare the median cases in Rhode Island in June, July, August and September. 
