
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 12: Predictive Modeling - Part 3"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment12.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data

```{r}
library(mlbench)
library(caret)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes



# Since the target variable is the 9th column of the dataset 9 must be in brackets
```

- Set seed to be 2020. 
```{r}
set.seed(2020)

```

- The target variable is `diabetes`
```{r}
names(df)[9] <- 'target'



```

- Partition the data into 80% training and 20% testing.  
```{r}
splitIndex <- createDataPartition(df$target, p = .80, 
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]



```


-------

2. Use cross-validation of 30 folds to tune random forest (method='rf').  What is the `mtry` value that produces the greatest accuracy?
```{r}
# The mtry of 2 has the greatest accuracy in the model


# Decide the range of the mtry to search for the best
tuneGrid = expand.grid(mtry = 1:15)
# Tell caret to do 10 - fold cross-Validation
trControl = trainControl(method = "cv",
                         number = 30)

# train a forest using above setup
forest_rf <- train(target~., data=df_train, 
                                method = "rf", 
                                trControl = trControl,
                                tuneGrid = tuneGrid)


plot(forest_rf)

```

 
-------

3. Use cross-validation with of 30 folds to tune random forest (method='ranger').  What are the parameters that produce the greatest accuracy?

```{r}

getModelInfo('ranger')$ranger$parameters

```



```{r}
trControl = trainControl(method = "cv",
                         number = 10)
tuneGrid = expand.grid(mtry = 2:8,
                       splitrule = c('gini', 'extratrees'),
                       min.node.size = c(1:10))
forest_ranger <- train(target~., data=df_train, 
                    method = "ranger", 
                    trControl = trControl,
                    tuneGrid = tuneGrid)


plot(forest_ranger)

```



-------

4. Go to https://topepo.github.io/caret/available-models.html and pick a classification model.  Tune the classification model using cross-validation of 30 folds. 

-------

5. Pick three models at [this link](https://topepo.github.io/caret/available-models.html) to compare using 15-fold cross validation method. Evaluate the accuracy of the final model on the test data. What is the best model?

-------

6. (Optional) Redo Question 5 on this following dataset. 

 - `Adult Census Income` dataset ([Link](https://www.kaggle.com/uciml/adult-census-income)) where the target variable is `income`
 
 -  `Credit card default` dataset ([link](https://www.kaggle.com/uciml/default-of-credit-card-clients-dataset)) where the target variable is `default.payment.next.month`