
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 9: Visualization - Revealing a graph"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment9.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```
```{r}
# Install the necessary libraries for use:

library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)
```


-------

1. Use the dataset by of covid 19 by WHO at https://covid19.who.int/WHO-COVID-19-global-data.csv. Find the three countries with the most numbers of deaths by Covid-19. 
```{r}
# Read the dataset into a dataframe:
covid_data <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")

# Observe the variables of the dataframe:

spec(covid_data)


```
```{r}
# look at examples of the data:


covid_data
```

Find the three countries with the most numbers of deaths by Covid-19.
```{r}
covid_data %>% 
  filter(Date_reported == '2021-10-31') %>%
  arrange(-Cumulative_deaths)

# According to the data the United States had the most number of cumulative
# deaths followed by Brazil and India.


```



Hint: 

-  Use `filter` to select the most current date
```{r}
# Use 10/31/2021

covid_data %>% 
  filter(Date_reported == '2021-10-31') # I am going to use halloween for this graph as it is better than 11/01/2021


```


-  Pipe with `arrange(-Cumulative_deaths)` to rank the data by the number of cumulative deaths
```{r}
# The resulting output are the countries that had the most number of cumulative deaths
# on the 31st of October 2021.

covid_data %>% 
  filter(Date_reported == '2021-10-31') %>% # <--- This is what the professor means by pipe function
  arrange(-Cumulative_deaths)
  
```


2. Make a plot revealing the number of deaths in the three countries with the most numbers of deaths
```{r}
covid_data %>% 
  filter(Country %in% c('United States of America','Brazil','India')) %>% 
  ggplot(aes(y=Cumulative_deaths,
            x=Date_reported,
            color=Country))+ 
  geom_line()+
  geom_point(size=3)+
  geom_text(aes(label = Cumulative_deaths), 
            hjust = -.1, size=5) +
  labs(title = 'Top 3 countries ranked by death counts', color='Country')+
  transition_reveal(Date_reported)


```


3. Create the new variable (column) `death_per_cases` recording the number of deaths per cases (Hint: divide cumulative deaths by cumulative cases).  What are the three countries with the highest deaths per cases?
```{r}
covid_data$death_per_cases <- (covid_data$Cumulative_deaths/covid_data$Cumulative_cases)


covid_data %>% 
  arrange(-death_per_cases) %>% select(death_per_cases, Country)

```


4. Make a plot revealing the number of deaths per cases of the US, Italy and Mexico. 

```{r}
covid_data %>% 
  filter(Country %in% c('United States of America','Italy','Mexico')) %>% 
  ggplot(aes(y=death_per_cases,
            x=Date_reported,
            color=Country))+ 
  geom_line()+
  geom_point(size=3)+
  geom_text(aes(label = death_per_cases), 
            hjust = -.1, size=5) +
  labs(title = 'Top 3 countries ranked by death counts', color='Country')+
  transition_reveal(Date_reported)
# Check with professor to make sure this is right 
```


5. Use `transition_reveal` to create three animated graph with the vaccination data at 

https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv

```{r}

new_covid <- read_csv("https://raw.githubusercontent.com/govex/COVID-19/master/data_tables/vaccine_data/us_data/time_series/vaccine_data_us_timeline.csv")

# Take a general look at the data:

new_covid

```

Graph 1:
```{r}

new_covid %>% 
  filter(Province_State %in% c('Alabama','Rhode Island','Louisiana')) %>% 
  ggplot(aes(y=Doses_admin, 
            x=Date,  
            color=Province_State))+
  geom_line()+
  geom_point(size=3)+
  geom_text(aes(label = Province_State),
            hjust = -.1, size=5) +
  labs(title = 'Vaccines', x='Date', y='Vaccines administered')+
  transition_reveal(Date)


```

Graph 2:
```{r}
new_covid %>% 
  ggplot(aes(y=Doses_admin, 
            x=Date))+ 
  geom_line()+
  geom_point(size=3)+
  geom_text(aes(label = Doses_admin), 
            hjust = -.1, size=5) +
  labs(title = 'Vaccines ', x='Date', y='Vaccines administered')+
  transition_reveal(Date) 


```





Graph 3: 


```{r}
# Observe the number of vaccines distributed in Nevada, California, and Utah

new_covid %>% 
  filter(Province_State %in% c('Nevada','California','Utah')) %>% 
  ggplot(aes(y=Doses_admin,
            x=Date, 
            color=Province_State))+
  geom_line()+
  geom_point(size=3)+
  geom_text(aes(label = Province_State),
            hjust = -.1, size=5) +
  labs(title = 'Vaccines', x='Date', y='Vaccines administered')+
  transition_reveal(Date)


```

