
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 11: Predictive Modeling - Part 2"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment11.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Blackboard.

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```


-------

1. Install the package `mlbench` and use the follows to import the data


# install.packages("mlbench") in R terminal completed

```{r}
library(mlbench)
data(PimaIndiansDiabetes)
df <- PimaIndiansDiabetes
```

- Set seed to be 2020. 

```{r}
set.seed(2020)


```




- The target variable is `diabetes`

```{r}
# Since diabetes is the 9th column I am going to rename it as the
# target variable
names(df)[9] <- 'target'


```



```{r}
# Check to make sure the target variable worked:

names(df)

```


- Partition the data into 80% training and 20% testing.

```{r}

library(caret)
splitIndex <- createDataPartition(df$target, p = 0.80,
                                  list = FALSE)
df_train <- df[ splitIndex,]
df_test <- df[-splitIndex,]

```


-------

2. Tuning Decision Tree:  Use cross-validation with 10 k-folds to find the maxdepth with the greatest accuracy. Plot the accuracy associated with different maxdepths against the maxdepths. The range to search for maxdepth is from 1 to 10. What is the selected maxdepth?

```{r}
# The maxdepth for this must be 1 through 10:
tuneGrid = expand.grid(maxdepth = 1:10)

# Use cross validation:
trControl = trainControl(method = "cv",
                         number = 10)

tree_approach2 <- train(target~., data = df_train,
                        method = "rpart2",
                        trControl = trControl,
                        tuneGrid = tuneGrid)




```



```{r}
# Plot the results from approach 2:

plot(tree_approach2)


```



```{r}

print(tree_approach2)


```


-------

3. Calculate the accuracy of the tuned decision tree in 2. on the test data.


```{r}
# Accuracy of the tuned decision tree from the previous problem is shown below:
pred <- predict(tree_approach2, df_test)
cm <- confusionMatrix(data = pred, reference = df_test$target, positive = "pos")
cm$overall[1]




```

