
---
output: 
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 8: Visualization - Making a bar race"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](fa2021_assignment8.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```
```{r}
library(tidyverse)
library(ggplot2)
library(lubridate)
```


-------

1. Install two packages `gganimate` and `gifski` then restart Rstudio. Use the WHO's dataset at [this link](https://covid19.who.int/WHO-COVID-19-global-data.csv). Make a top-10 bar race by months between countries on the number of deaths by Covid 19.  
```{r}
library(gapminder)
library(gganimate)
library(ggplot2)
library(tidyverse)
library(lubridate)
library(knitr)


```
```{r}

```
```{r}
# Read in the dataset:

df <- read_csv("https://covid19.who.int/WHO-COVID-19-global-data.csv")




```




2. Make another bar race using that dataset.  
```{r}
library(lubridate)
df$week <- week(df$Date_reported)
d1 <- df %>% group_by(week, Country) %>% summarise(mean = mean(Cumulative_deaths))
d2 <- d1 %>% group_by(week) %>% mutate(rank=rank(-mean)) %>% ungroup()
d3 <- d2 %>% filter(rank <= 10)
a1 <- d3 %>% ggplot(aes(x=rank, y=mean, group=Country, fill=Country, label=Country)) + geom_col()+
    geom_text(aes(y = mean, label = Country), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+
    labs(title = 'Week {closest_state}', x='', y='Total Number of Positive Caeses', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank()) + 
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)

```


3. Make a bar race using a dataset of your own interest. You may use the dataset that we use in class (https://covidtracking.com/data/download/all-states-history.csv) but you should make a different bar racev from ones in the slides. 

```{r}
new_bar <- read_csv("https://covidtracking.com/data/download/all-states-history.csv")

new_bar
```




```{r}

library(lubridate)
new_bar$week <- week(new_bar$date)
d_1 <- new_bar %>% group_by(week, state) %>% summarise(mean = mean(hospitalized))
d_2 <- d_1 %>% group_by(week) %>% mutate(ranks=rank(-mean)) %>% ungroup()
d_3 <- d_2 %>% filter(ranks <= 10)
a_1 <- d_3 %>% ggplot(aes(x=ranks, y=mean, group=state, fill=state, label=state)) + geom_col()+
    geom_text(aes(y = mean, label = state), hjust = 1.4)+ 
    coord_flip(clip = "off", expand = FALSE) +scale_x_reverse()+ 
    labs(title = 'Week {closest_state}', x='Total Number of hospitalized cases', y='', fill='state')+
    theme(plot.title = element_text(hjust = 1, size = 22),
          axis.ticks.y = element_blank(),
          axis.text.y  = element_blank())+
    transition_states(week)+
    ease_aes("cubic-in-out")
animate(a1, nframes = 400)
```

